---
title: "Schedule"
description: |
  Schedule for DS190, Capstone in Data Science, Pomona College, Fall 2025
format:
  html:
    code-fold: true
    html-math-method: katex
execute: 
  message: false
  warning: false
---


```{r}
#| echo: false
library(tidyverse)
library(fontawesome)
fontawesome::fa_html_dependency()
```

Here is your roadmap for the semester! 

-  On some days, there are <i class="fas fa-pencil-alt"></i> assignments due. Pay attention to due dates as you are graded **entirely** on turning in assignments on time (reasonable person test).

-  You will give three <i class = "fa-solid fa-microphone"></i> presentations. Two will be ~10 minutes, informal, and take place during regular class times. The final presentation will be ~20 minutes, more formal, and take place during reading days / finals week.

-  Five class periods will be based on disciplinary data science ethics. You are expected to <i class="fas fa-book-open"></i> read the pre-class materials and be an active <i class="fa-solid fa-comments"></i> participant in the class discussion. 

-   Attendance and class participation is mandatory. 


<!--
In order to use the icons, you need the fontawesome extension, https://github.com/quarto-ext/fontawesome

quarto add quarto-ext/fontawesome
-->


```{r}
#| echo: false
schedule <- tribble(
  ~`date`, ~topic, ~`assignment`,  ~readings,
  "Week 1 <br> 8.26.25", 'introductions + syllabus + logistics + pre-course survey', 
  ' ',
  '<a href="https://ds190-capstone.netlify.app/slides/2025-08-26-intro.html" target = "_blank"><i class="fa-solid fa-desktop"></i> Introduction</a>',
  
   "Week 2 <br> 9.2.25", 'check-in + citations + scripting + Git', 
  '<a href = "https://ds190-capstone.netlify.app/assignments" target = "_blank"><i class="fas fa-pencil-alt"></i> capstone topic</a>',
  '<a href="https://ds190-capstone.netlify.app/slides/2025-09-02-writing.html" target = "_blank"><i class="fa-solid fa-desktop"></i> Writing & Presenting</a> <br> <a href="https://ds190-capstone.netlify.app/slides/bibtex_example.qmd" target = "_blank"><i class="fa-solid fa-book-open"></i> BibTeX example</a> <br> <a href="https://ds190-capstone.netlify.app/slides/capstone.bib" target = "_blank"><i class="fa-solid fa-book-open"></i> .bib file</a>',
  
   "Week 3 <br> 9.9.25", '<i class="fa-solid fa-comments"></i> EDS - history', 
  '<a href = "https://ds190-capstone.netlify.app/assignments" target = "_blank"><i class="fas fa-pencil-alt"></i> annotated bibliography</a>',

  '<i class="fa-solid fa-book-open"></i> Clever, Iris.  2023.  <a href = "https://www.journals.uchicago.edu/doi/10.1086/723686" target = "_blank">"Biometry against Fascism: Geoffrey Morant, Race, and Anti-Racism in Twentieth-Century Physical Anthropology."</a>  Isis.<br> <i class="fa-solid fa-book-open"></i> Van Noorden, Richard.  2020.  "The Ethical Questions That Haunt Facial-Recognition Research." Nature. <a href="https://library.claremont.edu/" target = "_blank">log in to the library to access the article</a> <br> <i class="fa-solid fa-book-open"></i> Johnson, Thaddeus L., and Natasha N. Johnson. 2023. <a href="https://www.scientificamerican.com/article/police-facial-recognition-technology-cant-tell-black-people-apart/" target = "_blank">Police Facial Recognition Technology Cant Tell Black People Apart.</a> Scientific American.',

     "Week 4 <br> 9.16.25", '1st presentation', 
  ' ',
  ' ',

  
     "Week 5 <br> 9.23.25", '1st presentation', 
  ' ',
  ' ',

  
     "Week 6 <br> 9.30.25", '<i class="fa-solid fa-comments"></i> EDS - linguistics', 
  '<a href = "https://ds190-capstone.netlify.app/assignments" target = "_blank"><i class="fas fa-pencil-alt"></i> 1st outline</a>',

  '<i class="fa-solid fa-book-open"></i> Bender, Emily M., Timnit Gebru, Angelina McMillan-Major, and Shmargaret Shmitchell. 2021. <a href = "https://doi.org/10.1145/3442188.3445922" target = "_blank">"On the Dangers of Stochastic Parrots: Can Language Models Be Too Big?"</a> Proceedings of the 2021 ACM Conference on Fairness, Accountability, and Transparency,610–23. FAccT ’21. New York, NY, USA: Association for Computing Machinery. <br> <i class="fa-solid fa-book-open"></i> Beacken, Gabrielle, and Matthias Becker. 2025. <a href = "https://www.techpolicy.press/chatbot-grok-doesnt-glitch-it-reflects-x/" target = "_blank">"Chatbot Grok Doesn’t Glitch—It Reflects X."</a> Tech Policy Press. <br>  <i class="fa-solid fa-book-open"></i> Holliday, Nicole. 2025. <a href = "https://www.tiktok.com/@mixedlinguist/video/7517374618101992734" target = "_blank">"If Not Language, Why Language-Shaped?"</a> TikTokvideo.',

  
     "Week 7 <br> 10.7.25", '<i class="fa-solid fa-comments"></i> EDS - philosophy', 
  '<a href = "https://ds190-capstone.netlify.app/assignments" target = "_blank"><i class="fas fa-pencil-alt"></i> section draft</a>',
  '<i class="fa-solid fa-book-open"></i> Johnson, G.M. 2023. "Are Algorithms Value-Free? Feminist Theoretical Virtues in Machine Learning." Journal of Moral Philosophy 21 (1-2): 27-61. <a href = "https://doi.org/10.1163/17455243-20234372" target = "_blank">https://doi.org/10.1163/17455243-20234372</a> <b>the pdf is available on Canvas!!!!</b> <br> <i class="fa-solid fa-book-open"></i> Dastin, J. (2018, October 11). <a href = "https://www.reuters.com/article/world/insight-amazon-scraps-secret-ai-recruiting-tool-that-showed-bias-against-women-idUSKCN1MK0AG/" target = "_blank">"Insight — Amazon scraps secret AI recruiting tool that showed bias against women."</a> Reuters. ',

      "10.14.25", 'fall break', 
  ' ',
  ' ',
  
     "Week 8 <br> 10.21.25", '2nd presentation', 
 ' ',
 ' ',
  
     "Week 9 <br> 10.28.25", '2nd presentation', 
 ' ',
 ' ',

  
     "Week 10 <br> 11.4.25", '<i class="fa-solid fa-comments"></i> EDS - psychology', 
  '<a href = "https://ds190-capstone.netlify.app/assignments" target = "_blank"><i class="fas fa-pencil-alt"></i> introduction or 2nd section</a>',
 ' ',
  
  
     "Week 11 <br> 11.11.25", 'check-in', 
  '<a href = "https://ds190-capstone.netlify.app/assignments" target = "_blank"><i class="fas fa-pencil-alt"></i> ethics component</a>',
 ' ',
  
  
     "Week 12 <br> 11.18.25", '<i class="fa-solid fa-comments"></i> EDS - economics', 
  '<a href = "https://ds190-capstone.netlify.app/assignments" target = "_blank"><i class="fas fa-pencil-alt"></i> project draft</a>',

 ' ',

      "11.25.25", 'Thanksgiving break', 
  ' ',
  ' ',  
  
      "12.2.25 (class) + 12.4.25 (2-4pm) + 12.9.25 (2-5pm)", 'final presentations', 
  ' ',
  ' ',
 
      "12.9.25", 'final write-up', 
  '<a href = "https://ds190-capstone.netlify.app/assignments" target = "_blank"><i class="fas fa-pencil-alt"></i> final write-up</a>',
  ' ' 
)
  
```

```{r}
#| echo: false
#| column: body-outset
# can also use column: screen-inset also the entire page??
# can use column: page for the entire page
# can use column: body-outset to bleed outside the center column of text
schedule |> 
  gt::gt() |> 
  gt::fmt_markdown(columns = everything()) |> 
    gt::cols_width(date ~ pct(15),
                 everything() ~ pct(21.25)) 
```





