---
title: "Schedule"
description: |
  Schedule for DS190, Capstone in Data Science, Pomona College, Fall 2025
format:
  html:
    code-fold: true
    html-math-method: katex
execute: 
  message: false
  warning: false
---


Here's your roadmap for the semester!
Every day:

* read the assigned items
* post one question to the Sakai wiki
* complete your task if you are contextualizing, discussing, or summarizing
* pay attention to due dates for written assignments

 Some general thoughts on <a href = "handouts/Discussion-Instructions.pdf" target = "_blank">discussions</a>


```{r}
#| echo: false
library(tidyverse)
#library(fontawesome)
#fontawesome::fa_html_dependency()
```

Here's your roadmap for the semester! Each day, follow the general process outlined below:

-   Enjoy the notes / text <i class="fas fa-book-open"></i>

-   Attend class, review the <i class="fas fa-pencil-alt"></i> worksheet and solutions if you have any questions after working on it during class.  <i class="fas fa-desktop"></i> Slides from class are linked below. 

-   Discuss the reflection questions <i class="fas fa-lightbulb"></i> and ethics considerations <i class="fas fa-balance-scale"></i> (see the <i class="fas fa-book-open"></i> <a href = "https://ds002r-fds.netlify.app/notes" target = "_blank">class notes</a>) with your classmates and professor.

-   The textbooks are <b> <a href = "https://mdsr-book.github.io/mdsr3e/" target = "_blank">Modern Data Science with R (MDSR), 3rd edition</a></b> by Baumer, Kaplan, and Horton and <b> <a href = "https://r4ds.hadley.nz/" target = "_blank">R for Data Science (R4DS), 2nd edition</a></b> by Wickham, Çetinkaya-Rundel, and Grolemund.

-   Homework assignments are found at the <a href = "https://github.com/orgs/ST47S-FODS-Spring2025/repositories" target = "_blank">GitHub course organization</a>.  Due dates are provided on each assignment (roughly every other week).  See the <a href = "https://ds002r-fds.netlify.app/github">course GitHub page</a> for more information on how to find, complete, and submit assignments.

<!--
In order to use the icons, you need the fontawesome extension, https://github.com/quarto-ext/fontawesome

quarto add quarto-ext/fontawesome
-->


```{r}
#| echo: false
schedule <- tribble(
  ~`date`, ~topic, ~`assignment`, ~`due dates`, ~readings,
  "Week 1 <br> 8.26.25", 'introductions + syllabus + logistics + pre-course survey', 
  ' ',
  ' ',
  ' ',
  
   "Week 2 <br> 9.02.25", 'check-in + citations + scripting + Git', 
  ' ',
  ' ',
  ' ',
  
   "Week 3 <br> 9.9.25", 'EDS - history', 
  ' ',
  ' ',
  ' ',

     "Week 4 <br> 9.16.25", '1st presentation', 
  ' ',
  ' ',
  ' ',

  
     "Week 5 <br> 9.23.25", '1st presentation', 
  ' ',
  ' ',
  ' ',

  
     "Week 6 <br> 9.30.25", 'EDS - linguistics', 
  '  ',
  ' ',
  ' ',

  
     "Week 7 <br> 10.07.25", 'EDS - philosophy', 
  ' ',
  ' ',
  ' ',

      "10.14.25", 'fall break', 
  ' ',
  ' ',
  ' ',
  
     "Week 8 <br> 10.21.25", '2nd presentation', 
 ' ',
 ' ',
 ' ',
  
     "Week 9 <br> 10.28.25", '2nd presentation', 
 ' ',
 ' ',
 ' ',

  
     "Week 10 <br> 11.04.25", 'EDS - psychology', 
 ' ',
 ' ',
 ' ',
  
  
     "Week 11 <br> 11.11.25", 'check-in', 
 ' ',
 ' ',
 ' ',
  
  
     "Week 12 <br> 11.18.25", 'EDS - economics', 
 ' ',
 ' ',
 ' ',

      "11.25.25", 'Thanksgiving break', 
  ' ',
  ' ',
  ' ',  
  
      "12.02.25 + 12.06.25 + 12.13.25", 'final presentations', 
  ' ',
  ' ',
  ' '
)
  
```

```{r}
#| echo: false
#| column: screen-inset
# can also use column: screen-inset also the entire page??
# can use column: page for the entire page
# can use column: body-outset to bleed outside the center column of text
schedule |> 
  gt::gt() |> 
  gt::fmt_markdown(columns = everything()) |> 
    gt::cols_width(date ~ pct(8),
                 everything() ~ pct(23)) 
```





