---
title: "Schedule"
description: |
  Schedule for DS190, Capstone in Data Science, Pomona College, Fall 2026
format:
  html:
    code-fold: true
    html-math-method: katex
execute: 
  message: false
  warning: false
---


```{r}
#| echo: false
library(tidyverse)
library(fontawesome)
fontawesome::fa_html_dependency()
```

Here is your roadmap for the semester! 

-  On some days, there are <i class="fas fa-pencil-alt"></i> assignments due. Pay attention to due dates as you are graded **entirely** on turning in assignments on time (reasonable person test).

-  You will give two <i class = "fa-solid fa-microphone"></i> presentations. One will be ~10 minutes, informal, and take place during regular class times. The final presentation will be ~20 minutes, more formal, and take place during reading days or during finals week.

-  Five class periods will be based on disciplinary data science ethics. You are expected to <i class="fas fa-book-open"></i> read the pre-class materials and be an active <i class="fa-solid fa-comments"></i> participant in the class discussion. 

-   Attendance and class participation is mandatory. 


<!--
In order to use the icons, you need the fontawesome extension, https://github.com/quarto-ext/fontawesome

quarto add quarto-ext/fontawesome
-->


```{r}
#| echo: false

# fmt: skip

schedule <- tribble(
  ~`date`, ~topic, ~`assignment`, ~readings ,
  "Week 1 <br> 9.1.26", 'introductions + syllabus + logistics + pre-course survey',
  ' ',
  '<a href="https://ds190-capstone.netlify.app/slides/2026-09-01-intro.html" target = "_blank"><i class="fa-solid fa-desktop"></i> Introduction</a>',

  "Week 2 <br> 9.8.26", '<i class="fa-solid fa-comments"></i> EDS - CS/engineering/chemistry <br> <a href = "https://www.cs.hmc.edu/~julie/" target = "_blank">Julie Modero</a>',
  '<a href = "https://ds190-capstone.netlify.app/assignments" target = "_blank"><i class="fas fa-pencil-alt"></i> capstone topic</a>',
  '<i class="fa-solid fa-book-open"></i>  Read <a href = "https://claremontcourier.com/latest-news/viewpoint-take-precautions-as-unhealthy-air-will-return-july-4-89090/" target = "_blank">op-ed by Prof. Medero and Prof. Hawkins</a> from Harvey Mudd’s LILAQ lab <br> <i class="fa-solid fa-book-open"></i> Read the EPA <a href="https://www.airnow.gov/aqi/aqi-basics/" target = "_blank">Air Quality Index (AQI) Basics</a> and <a href="https://www.airnow.gov/aqi/aqi-basics/using-air-quality-index/" target = "_blank">Using Air Quality Index pages</a> <br> <i class="fa-solid fa-book-open"></i> Skim the <a href="https://usepa.servicenowservices.com/airnow/en/how-is-the-nowcast-algorithm-used-to-report-current-air-quality?id=kb_article_view&sys_id=798ba26c1b1a5ed079ab0f67624bcb6d&spa=1" target = "_blank">explanation of how NowCast is calculated</a>, don’t worry about understanding the details, just get an impression',

  "Week 3 <br> 9.15.26", '<i class="fa-solid fa-comments"></i> EDS - philosophy <br> <a href = "https://julie-tannenbaum.sites.pomona.edu/" target = "_blank">Julie Tannenbaum</a>',
  '<a href = "https://ds190-capstone.netlify.app/assignments" target = "_blank"><i class="fas fa-pencil-alt"></i> annotated bibliography</a>',
  '<i class="fa-solid fa-book-open"></i> And Justice for All: New Introductory Essays in Ethics and Public Police, 1982, eds. Tom Regan and Donald VanDeVeer <a href = "https://pomona.instructure.com/courses/7644/files/folder/Uploaded%20Media?preview=580998" target = "_blank">Chapter 9 Utilitarianism</a>, Dan Brock',

  # ask Sara Sadhwani to speak???
  # Macdonell, W. R. (1902). On criminal anthropometry and the identification of criminals. Biometrika, 1(2), 177–227.
  # Green, Ben. "Data Science as Political Action: Grounding Data Science in a Politics of Justice." Journal of Social Computing, vol. 2, no. 3, Sept. 2021, pp. 249–265. https://doi.org/10.23919/JSC.2021.0029.  (I'm not sure that it is the right article, but it is an excellent article and maybe even better than the one quoted below.)

  # Green argues that all data science work inherently involves political choices and value judgments about how society should function, even when practitioners don’t recognize this dimension of their work. “On criminal anthropometry and the identification of criminals,” an experiment conducted by W. R. MacDonnell in 1902 as part of Biometrika, demonstrates an early example of how ignorance towards ethical principles and misplaced partiality can depreciate an experiment’s insights and credibility over time.

  # Using “Head Length, Head Breadth, Face Breadth, Left Middle Finger, Left Cubit, Left Foot, and Height, of each [observed] individual” to classify and identify potential “criminal classes” and genetic (and environmental) predispositions to crime, this early form of data-driven classification attempted to use statistics and arbitrary measurements to distinguish “habitual criminals” from “non-habitual criminals” and differentiate both groups from the general population, demonstrating an early application of using data to categorize (and police) people.

  "Week 4 <br> 9.22.26", 'check-ins + citations + scripting + Git',
  ' ',
  '<a href="https://ds190-capstone.netlify.app/slides/2025-09-02-writing.html" target = "_blank"><i class="fa-solid fa-desktop"></i> Writing & Presenting</a> <br> <a href="https://ds190-capstone.netlify.app/slides/bibtex_example.qmd" target = "_blank"><i class="fa-solid fa-book-open"></i> BibTeX example</a> <br> <a href="https://ds190-capstone.netlify.app/slides/capstone.bib" target = "_blank"><i class="fa-solid fa-book-open"></i> .bib file</a>',

  "Week 5 <br> 9.29.26", '<i class="fa-solid fa-comments"></i> EDS - CARE & FAIR',
  ' ',
  '<i class="fa-solid fa-book-open"></i> Carroll, S. R., Rodriguez-Lonebear, D., & Martinez, A. (2019). Indigenous data governance: Strategies from United States Native Nations. Data Science Journal, 18(1), 31.  <a href = "https://doi.org/10.5334/dsj-2019-031" target = "_blank">https://doi.org/10.5334/dsj-2019-031</a> <br> <i class="fa-solid fa-book-open"></i> Carroll, S.R., Herczog, E., Hudson, M. et al. Operationalizing the CARE and FAIR Principles for Indigenous data futures. Sci Data 8, 108 (2021). <a href = "https://doi.org/10.1038/s41597-021-00892-0" target = "_blank">https://doi.org/10.1038/s41597-021-00892-0</a> <br> <i class="fa-solid fa-book-open"></i> Markkula Center for Applied Ethics. (n.d.). Introduction of An Introduction to Data Ethics. Santa Clara University. <a href = "https://www.scu.edu/media/ethics-center/technology-ethics/IntroToDataEthics.pdf" target = "_blank">https://www.scu.edu/media/ethics-center/technology-ethics/IntroToDataEthics.pdf</a>',

  "Week 6 <br> 10.6.26", '<i class="fa-solid fa-comments"></i> EDS - ecology <br> <a href = "https://www.pomona.edu/directory/people/wallace-meyer" target = "_blank">Marty Meyer</a>',
  '<a href = "https://ds190-capstone.netlify.app/assignments" target = "_blank"><i class="fas fa-pencil-alt"></i> 1st outline</a>',
  '<i class="fa-solid fa-book-open"></i>  <a href = "" target = "_blank">Reading 1</a>  <br> <i class="fa-solid fa-book-open"></i> <a href="" target = "_blank">Reading 2</a>',

  "Week 7 <br> 10.13.26", 'presentations',
  '<a href = "https://ds190-capstone.netlify.app/assignments" target = "_blank"><i class="fas fa-pencil-alt"></i> section draft</a>',
  ' ',

  "Week 8 <br> 10.20.26", 'fall break <br> no class meeting',
  'one-on-one check-ins with Prof Hardin',
  ' ',

  "Week 9 <br> 10.27.26", 'presentations',
  ' ',
  ' ',

  "Week 10 <br> 11.3.26", 'presentations',
  '<a href = "https://ds190-capstone.netlify.app/assignments" target = "_blank"><i class="fas fa-pencil-alt"></i> introduction or 2nd section</a>',
  ' ',

  "Week 11 <br> 11.10.26", 'presentations',
  '<a href = "https://ds190-capstone.netlify.app/assignments" target = "_blank"><i class="fas fa-pencil-alt"></i> ethics component</a>',
  ' ',

  "Week 12 <br> 11.17.26", 'presentations',
  ' ',
  ' ',

  "Week 13 <br> 11.24.26" , 'Thanksgiving break <br> no class meeting',
  '<a href = "https://ds190-capstone.netlify.app/assignments" target = "_blank"><i class="fas fa-pencil-alt"></i> project draft</a> due Monday 11.23.26',
  ' ',

  "Week 14 <br> 12.1.26", '<i class="fa-solid fa-comments"></i> EDS - linguistics <br> <a href = "https://www.pomona.edu/directory/people/ernesto-gutierrez-topete" target = "_blank">Ernesto Gutiérrez Topete</a>',
  ' ',
  '<i class="fa-solid fa-book-open"></i> Bender, Emily M., Timnit Gebru, Angelina McMillan-Major, and Shmargaret Shmitchell. 2021. <a href = "https://doi.org/10.1145/3442188.3445922" target = "_blank">On the Dangers of Stochastic Parrots: Can Language Models Be Too Big?</a> Proceedings of the 2021 ACM Conference on Fairness, Accountability, and Transparency,610–23. FAccT ’21. New York, NY, USA: Association for Computing Machinery. <br> <i class="fa-solid fa-book-open"></i> Beacken, Gabrielle, and Matthias Becker. 2025. <a href = "https://www.techpolicy.press/chatbot-grok-doesnt-glitch-it-reflects-x/" target = "_blank">Chatbot Grok Doesn’t Glitch—It Reflects X.</a> Tech Policy Press. <br>  <i class="fa-solid fa-book-open"></i> Holliday, Nicole. 2025. <a href = "https://www.tiktok.com/@mixedlinguist/video/7517374618101992734" target = "_blank">If Not Language, Why Language-Shaped?</a> TikTok video.',

  "Week 15 <br> 12.8.26", 'wrap-up',
  '<a href = "https://ds190-capstone.netlify.app/assignments" target = "_blank"><i class="fas fa-pencil-alt"></i> final presentations</a>',
  '12.10.26 (2-5pm) or <br> 12.14.26 (2-5pm)',

  "12.14.26", 'final write-up',
  '<a href = "https://ds190-capstone.netlify.app/assignments" target = "_blank"><i class="fas fa-pencil-alt"></i> final write-up</a>',
  ' '
)
```

```{r}
#| echo: false
#| column: body-outset
# can also use column: screen-inset also the entire page??
# can use column: page for the entire page
# can use column: body-outset to bleed outside the center column of text
schedule |>
  gt::gt() |>
  gt::fmt_markdown(columns = everything()) |>
  gt::cols_width(date ~ pct(15), everything() ~ pct(21.25))
```





